An Engineered Empirical Burnstein Bound

### 2018-08-17 paper/main.tex
updated paper

		(0.005, 31.33262397944378)(0.01, 34.72886250674945)(0.015, 36.909296945183726)(0.02, 38.627583846687266)(0.025, 39.59462124039761)

@@

		\node [above] at (endofplotsquare) {$n=25$};

@@

		(0.005, 28.333532153239666)(0.01, 31.153830409409)(0.015, 32.87549096079947)(0.02, 33.81992265562242)(0.025, 34.89945361309619)(0.03, 35.74891595008532)(0.035, 36.60739883058407)(0.04, 37.276099921865196)(0.045, 37.59026746494855)(0.05, 38.218754538940686)(0.055, 38.83065159779602)(0.06, 39.39861647873854)(0.065, 39.910212250065214)

@@

		\node [above] at (endofplotsquare) {$n=50$};

@@

		(0.005, 30.038701393161688)(0.01, 31.412520149627277)(0.015, 32.49171315420119)(0.02, 32.876510879893)(0.025, 33.61899806422779)(0.03, 34.07734163182933)(0.035, 34.27418933046886)(0.04, 34.76092837396386)(0.045, 35.00082505166452)(0.05, 35.60742157468709)(0.055, 36.00845546401498)(0.06, 36.09363022383078)(0.065, 36.49561598871189)(0.07, 36.871363860949025)(0.075, 36.995564126738095)(0.08, 37.25705721710657)(0.085, 37.63281018078307)(0.09, 37.94537201050319)(0.095, 38.313563615135976)(0.1, 38.57428091364722)(0.105, 38.898129385115695)(0.11, 38.919035439297076)

@@

		\node [above] at (endofplotsquare) {$n=100$};

@@

		(0.005, 31.585709637284875)(0.01, 32.14640200496432)(0.015, 32.480242185958275)(0.02, 32.72477439020389)(0.025, 32.85137640603805)(0.03, 33.164192395805884)(0.035, 33.41972794004208)(0.04, 33.34159833965975)(0.045, 33.824240924074424)(0.05, 33.77957868846732)(0.055, 34.028900979162536)(0.06, 34.23479104354531)(0.065, 34.320408892537166)(0.07, 34.556516165135605)(0.075, 34.775904883097695)(0.08, 34.98535349546355)(0.085, 35.19862669231675)(0.09, 35.3945988354474)(0.095, 35.601977507693036)(0.1, 35.72487858163208)(0.105, 35.83625307070917)(0.11, 36.04135799347741)(0.115, 36.25828614993272)(0.12, 36.48817284893286)(0.125, 36.73194354036559)(0.13, 36.91341720219515)(0.135, 37.18914713784862)(0.14, 37.407683615789495)(0.145, 37.415360037546876)

@@

		\node [above] at (endofplotsquare) {$n=200$};

@@

		(0.005, 30.95805680601551)(0.01, 31.852731472234087)(0.015, 31.65165353001502)(0.02, 31.838019953330228)(0.025, 31.80514856457896)(0.03, 32.049553438239556)(0.035, 31.874671808872318)(0.04, 32.15628114167258)(0.045, 32.18970870320976)(0.05, 32.29347571578702)(0.055, 32.328022832020885)(0.06, 32.32551565971646)(0.065, 32.51203709690735)(0.07, 32.671571263469616)(0.075, 33.00950294213178)(0.08, 32.921019505844626)(0.085, 33.017153308081845)(0.09, 33.11615572233624)(0.095, 33.393651317961485)(0.1, 33.19788472106813)(0.105, 33.458020247263455)(0.11, 33.5638596989855)(0.115, 33.685389159897156)(0.12, 33.74232351659747)(0.125, 33.86778330552732)(0.13, 34.01232127428546)(0.135, 34.31523066744031)(0.14, 34.360222768291344)(0.145, 34.35739937066466)(0.15, 34.42537992870109)(0.155, 34.52118296490931)(0.16, 34.64446824473269)(0.165, 34.79488974531291)(0.17, 34.972098710274665)(0.175, 35.1757460413815)(0.18, 35.294877117787664)

@@

		\node [above] at (endofplotsquare) {$n=500$};

@@

		(0.005, 30.260287580516597)(0.01, 31.072712082932913)(0.015, 30.438989170134068)(0.02, 31.07887032375107)(0.025, 31.03408484266436)(0.03, 30.826085689381884)(0.035, 31.046097650764082)(0.04, 31.154259509093446)(0.045, 31.016858116914054)(0.05, 31.183097869794107)(0.055, 31.225975525465564)(0.06, 31.23249090698877)(0.065, 31.428023434202135)(0.07, 31.489666903553392)(0.075, 31.56173735319704)(0.08, 31.761301359885042)(0.085, 31.729964289057005)(0.09, 31.886510772066785)(0.095, 32.04347363722421)(0.1, 32.20435818840492)(0.105, 32.371965761927385)(0.11, 32.21538679904917)(0.115, 32.38001692151431)(0.12, 32.48085273757601)(0.125, 32.525780745561875)(0.13, 32.54658216492318)(0.135, 32.74841841730962)(0.14, 32.73824299176051)(0.145, 32.744293569773916)(0.15, 32.7796880354745)(0.155, 32.844022563820616)(0.16, 32.936888670494405)(0.165, 33.05787673349303)(0.17, 33.027986659386485)(0.175, 33.20865432723783)(0.18, 33.246662344351044)(0.185, 33.484850761982344)(0.19, 33.58811058089041)(0.195, 33.72513316286922)(0.2, 33.74255294433519)

@@

		\node [below] at (endofplotsquare) {$n=1000$};

@@

		(0.0, 100.0)(0.005, 76.80881648298994)(0.01, 70.80012751036021)(0.015, 66.60353535353535)(0.02, 62.960629921259844)(0.025, 59.830268741159834)(0.03, 57.38265464718681)(0.035, 54.86272684969753)(0.04, 52.966426490878426)(0.045, 50.833715771760744)(0.05, 49.34260238778903)(0.055, 47.48114630467571)(0.06, 46.261543044384865)(0.065, 45.21393912659903)(0.07, 43.60780860120358)(0.075, 42.741234424804404)(0.08, 41.970541970541966)(0.085, 41.27275292789615)(0.09, 41.34324249931186)(0.095, 40.828241683638836)(0.1, 40.36967586391642)(0.105, 40.67885117493473)(0.11, 40.33732457834427)(0.115, 40.80762478053674)(0.12, 41.318681318681314)(0.125, 41.896387832699624)(0.13, 42.54679916801479)(0.135, 43.2678270634475)(0.14, 44.87427466150871)(0.145, 46.60652040188641)(0.15, 48.55862874951305)(0.155, 50.767251676927316)(0.16, 53.47442378545112)(0.165, 59.068590983484604)
			}node[pos=0.7](endofplotsquare){} ;
		\node [above right] at (endofplotsquare) {$n=10$};

@@

		(0.0, 100.0)(0.005, 77.6561403508772)(0.01, 71.34845838015866)(0.015, 66.77283196861327)(0.02, 62.981189851268596)(0.025, 60.0)(0.03, 57.0902927514777)(0.035, 54.45127942244435)(0.04, 51.96859607876512)(0.045, 49.97258771929825)(0.05, 47.57404572092287)(0.055, 45.676705541500894)(0.06, 43.987817089452605)(0.065, 42.12854540723393)(0.07, 40.28687246647957)(0.075, 38.81136950904393)(0.08, 36.880072137060424)(0.085, 35.22028211023427)(0.09, 33.87552312037438)(0.095, 32.53546508941362)(0.1, 30.81437249047669)(0.105, 28.95112416489131)(0.11, 27.395132055929572)(0.115, 26.174496644295303)(0.12, 24.903425186711306)(0.125, 23.670007710100233)(0.13, 23.065173116089614)(0.135, 21.940071102082275)(0.14, 20.811153358681874)(0.145, 20.550688360450565)(0.15, 19.490254872563717)(0.155, 19.37869822485207)(0.16, 19.30933852140078)(0.165, 19.34787820666507)(0.17, 19.38534278959811)(0.175, 20.506329113924053)(0.18, 20.644283121597095)(0.185, 22.798605056669572)(0.19, 24.916247906197654)(0.195, 27.07537688442211)(0.2, 31.11861861861862)(0.205, 35.2304469273743)(0.21, 41.46645865834633)(0.215, 51.718869365928185)
			}node[pos=0.7](endofplotsquare){} ;
		\node [above right] at (endofplotsquare) {$n=25$};

@@

		(0.0, 100.0)(0.005, 73.41959943954505)(0.01, 66.4436173582515)(0.015, 61.55984585594049)(0.02, 57.93403164698015)(0.025, 54.687443245795656)(0.03, 51.969260326609025)(0.035, 49.440167949615116)(0.04, 47.26428079834825)(0.045, 45.52155103348822)(0.05, 43.63969363969365)(0.055, 41.895873454808815)(0.06, 40.23579989577905)(0.065, 38.6774968170317)(0.07, 37.13806461919406)(0.075, 36.073059360730596)(0.08, 34.695663042119726)(0.085, 33.263492802545294)(0.09, 31.835726416550862)(0.095, 30.517167250168896)(0.1, 29.4787827093551)(0.105, 27.9820525495266)(0.11, 27.141351798886053)(0.115, 25.998680422264876)(0.12, 25.14569457659372)(0.125, 23.599320882852297)(0.13, 22.825830083894598)(0.135, 21.39899438036083)(0.14, 20.631424375917767)(0.145, 19.502512341971507)(0.15, 18.148213342721355)(0.155, 17.384900322293685)(0.16, 16.283268301205524)(0.165, 14.950369495824049)(0.17, 13.428466886205634)(0.175, 12.641165755919854)(0.18, 11.73265528514348)(0.185, 10.732414793328498)(0.19, 10.808876163206872)(0.195, 9.896391568417291)(0.2, 10.109193377949982)(0.205, 11.514736120630568)(0.21, 13.028990336554482)(0.215, 15.574032619123763)(0.22, 21.29793510324484)(0.225, 28.771466314398943)(0.23, 40.30243261012492)
			}node[pos=0.745](endofplotsquare){} ;
		\node [above] at (endofplotsquare) {$n=50$};
		(0.0, 100.0)(0.005, 66.63264504985476)(0.01, 59.04596954607779)(0.015, 53.999488883209814)(0.02, 50.347727640304065)(0.025, 47.17075223238636)(0.03, 44.61167971101746)(0.035, 42.5287356321839)(0.04, 40.44242768009076)(0.045, 38.82229464729603)(0.05, 36.95086234949561)(0.055, 35.37062155908402)(0.06, 34.21394768318686)(0.065, 32.83438879293802)(0.07, 31.577620967741936)(0.075, 30.56930693069307)(0.08, 29.513914294773297)(0.085, 28.306342780027)(0.09, 27.2679657647577)(0.095, 26.1414503133393)(0.1, 25.240174672489086)(0.105, 24.242424242424242)(0.11, 23.719661228897856)(0.115, 22.66414141414141)(0.12, 21.690588327422837)(0.125, 20.795378804710058)(0.13, 19.986774673499745)(0.135, 19.030112044817923)(0.14, 18.19329010922065)(0.145, 17.679088336256697)(0.15, 16.523420713364853)(0.155, 15.733937115516067)(0.16, 15.263202437373053)(0.165, 14.070096816471484)(0.17, 13.594470046082947)(0.175, 12.479061976549408)(0.18, 11.941848390446522)(0.185, 10.83476924993254)(0.19, 10.110966462091636)(0.195, 9.32322149863986)(0.2, 8.034350357128114)(0.205, 6.9143446852425186)(0.21, 6.365503080082135)(0.215, 5.532786885245901)(0.22, 5.906108026249369)(0.225, 6.26865671641791)(0.23, 10.4)(0.235, 19.900083263946712)(0.24, 39.94439295644115)

@@

		(0.0, 100.0)(0.005, 58.98664343786295)(0.01, 50.57766367137355)(0.015, 45.77709671715683)(0.02, 42.100909842845326)(0.025, 39.265978521530606)(0.03, 36.95646756871246)(0.035, 34.86590038314177)(0.04, 33.287324591672416)(0.045, 31.549749463135292)(0.05, 30.303030303030305)(0.055, 28.925445534113674)(0.06, 27.7629141798724)(0.065, 26.8988231513837)(0.07, 25.831202046035806)(0.075, 24.751099791618426)(0.08, 23.846328711070697)(0.085, 22.90933467404057)(0.09, 22.152617503755)(0.095, 21.356421356421354)(0.1, 20.641965664778876)(0.105, 19.924470242674317)(0.11, 19.246298788694478)(0.115, 18.532910658894913)(0.12, 17.784217265314382)(0.125, 17.0)(0.13, 16.44693473961766)(0.135, 15.58770225480432)(0.14, 14.952787478980731)(0.145, 14.591315453384416)(0.15, 14.068681753441997)(0.155, 13.438921122785)(0.16, 12.576495566379412)(0.165, 12.1045477014335)(0.17, 11.67240719479524)(0.175, 10.71428571428572)(0.18, 10.216812015503878)(0.185, 9.878838771593088)(0.19, 8.965888367365245)(0.195, 8.532969639468684)(0.2, 7.883082373782105)(0.205, 7.0957119967072035)(0.21, 6.501031561388886)(0.215, 5.830903790087479)(0.22, 4.503241633082184)(0.225, 3.994190268700073)(0.23, 3.258508327299059)(0.235, 3.7089871611982885)(0.24, 9.308510638297872)(0.245, 38.92587660896582)

@@

		(0.0, 100.0)(0.005, 48.82985928211302)(0.01, 40.20061728395061)(0.015, 35.8974358974359)(0.02, 32.10526315789474)(0.025, 29.89508775370134)(0.03, 27.697441601779754)(0.035, 26.26728110599078)(0.04, 24.66329966329966)(0.045, 23.238526179702653)(0.05, 22.453433091730965)(0.055, 21.28060263653484)(0.06, 20.47278564132497)(0.065, 19.744318181818187)(0.07, 18.640077551585644)(0.075, 17.621533663299214)(0.08, 17.415433403805487)(0.085, 16.612798965740136)(0.09, 16.096757852076994)(0.095, 15.320195510725066)(0.1, 15.115005476451262)(0.105, 14.304548450889918)(0.11, 13.963287073867834)(0.115, 13.283062645011604)(0.12, 12.956621004566218)(0.125, 12.517580872011253)(0.13, 12.032412032412036)(0.135, 11.314900744076228)(0.14, 10.927008880225257)(0.145, 10.857264866019005)(0.15, 10.408432147562582)(0.155, 10.170285892829247)(0.16, 9.61994026161294)(0.165, 9.276248725790005)(0.17, 8.879802110151953)(0.175, 8.181135851888914)(0.18, 7.840951319212183)(0.185, 7.4437788470980895)(0.19, 7.141815353201405)(0.195, 6.774544137181502)(0.2, 6.153993855606756)(0.205, 5.965045592705168)(0.21, 5.580409700965385)(0.215, 4.929577464788732)(0.22, 4.562383612662934)(0.225, 3.944315545243619)(0.23, 2.784222737819025)(0.235, 2.7586206896551726)(0.24, 2.059496567505721)(0.245, 4.0)

@@

		\node [below left] at (endofplotsquare) {$n=1000$};

@@

		\caption{The percent reduction in the 0.5 probability bound, that going from our EBB to Hoeffding's inequality (representing perfect knowledge of the variance, $\hat{\sigma}^2=\sigma^2$) achieves, for various n=10,25,50,100,200,500,1000.}

>>>>

(0.0, 5.68279906803574)(0.005, 21.836118930505265)(0.01, 25.802823484071254)(0.015, 28.022512115598744)(0.02, 29.864039382966602)(0.025, 31.111321132916768)(0.03, 32.0919738463798)(0.035, 33.05847784139354)(0.04, 33.736278995225796)(0.045, 34.440280964621486)(0.05, 35.15592306441015)(0.055, 35.64597513743734)(0.06, 36.16219390744528)(0.065, 36.685357809102705)

@@

		\node [above] at (endofplotsquare) {$\scriptstyle n=50$};

@@

(0.0, 5.854298988166525)(0.005, 23.964254032213393)(0.01, 27.37245164317984)(0.015, 29.355131457208117)(0.02, 30.91363823414449)(0.025, 31.790584639065834)(0.03, 32.66128510303768)(0.035, 33.26400387886201)(0.04, 33.92107357684253)(0.045, 34.471764641790685)(0.05, 34.8305410962864)(0.055, 35.36497453138069)(0.06, 35.79802010253675)(0.065, 36.02369268944928)(0.07, 36.377072129280634)(0.075, 36.79581728264095)(0.08, 37.15435342833946)(0.085, 37.50755150324622)(0.09, 37.848233168432564)

@@

		\node [above] at (endofplotsquare) {$\scriptstyle n=75$};

@@

(0.0, 6.832182513392391)(0.005, 25.52090535766474)(0.01, 28.650608209343815)(0.015, 30.50309695254201)(0.02, 31.50863773916302)(0.025, 32.33004657032931)(0.03, 33.029564280282244)(0.035, 33.44221704351276)(0.04, 33.965329939500016)(0.045, 34.30605952371319)(0.05, 34.692416934952185)(0.055, 35.160885337710546)(0.06, 35.45220688581006)(0.065, 35.903347122285375)(0.07, 36.23498648051504)(0.075, 36.37175783096322)(0.08, 36.65259726736771)(0.085, 36.988036601825)(0.09, 37.26282798128783)(0.095, 37.544772095379265)(0.1, 37.60863642146002)(0.105, 37.904706139336135)(0.11, 38.1586914821099)

@@

		\node [above right] at (endofplotsquare) {$\scriptstyle n=100$};

@@

(0.0, 7.693682332229607)(0.005, 27.990066618755765)(0.01, 30.446803018183655)(0.015, 31.488910428759073)(0.02, 32.375218883686195)(0.025, 32.767178192308855)(0.03, 33.24333663177549)(0.035, 33.51602854693247)(0.04, 33.87791050108074)(0.045, 34.016628689572016)(0.05, 34.273764717129254)(0.055, 34.575402898651696)(0.06, 34.927925485299724)(0.065, 35.1528833291239)(0.07, 35.44618521289669)(0.075, 35.63701544350516)(0.08, 35.90448901985416)(0.085, 36.16597179371182)(0.09, 36.167776741773636)(0.095, 36.40559868439304)(0.1, 36.64827000607862)(0.105, 36.82647424171691)(0.11, 37.02387109415649)(0.115, 37.08745263644369)(0.12, 37.31109551975997)(0.125, 37.486455368251484)(0.13, 37.69786237630875)

@@

		\node [above right] at (endofplotsquare) {$\scriptstyle n=150$};

@@

(0.0, 8.943146707982761)(0.005, 29.201936453915007)(0.01, 31.11204837699122)(0.015, 31.91913616534297)(0.02, 32.552273811717235)(0.025, 32.609834594548985)(0.03, 33.164192395805884)(0.035, 33.41972794004208)(0.04, 33.34159833965974)(0.045, 33.824240924074424)(0.05, 33.77957868846732)(0.055, 34.028900979162536)(0.06, 34.23479104354531)(0.065, 34.32040889253717)(0.07, 34.556516165135605)(0.075, 34.775904883097695)(0.08, 34.98535349546355)(0.085, 35.19862669231675)(0.09, 35.3945988354474)(0.095, 35.601977507693036)(0.1, 35.72487858163208)(0.105, 35.83625307070917)(0.11, 36.04135799347741)(0.115, 36.174635606822406)(0.12, 36.40685168740781)(0.125, 36.65285846979104)(0.13, 36.83648234512465)(0.135, 37.03941924068021)(0.14, 37.26195063235711)(0.145, 37.433344129490116)

@@

		\node [right] at (endofplotsquare) {$\scriptstyle n=200$};

@@

(0.0, 9.324714689596224)(0.005, 30.095584441654534)(0.01, 31.606829627205162)(0.015, 32.244548074817345)(0.02, 32.319578663450045)(0.025, 32.58807145785705)(0.03, 32.54223055419724)(0.035, 32.74254561191743)(0.04, 32.71082614646207)(0.045, 32.945140817400365)(0.05, 33.26420226830405)(0.055, 33.352403581449735)(0.06, 33.26484741097522)(0.065, 33.4364755257399)(0.07, 33.542579090314256)(0.075, 33.65929472234714)(0.08, 33.90576069594512)(0.085, 34.14334017925624)(0.09, 34.08757080939384)(0.095, 34.29799190734557)(0.1, 34.512134923158726)(0.105, 34.73247721906126)(0.11, 34.70947485893356)(0.115, 34.923922016875885)(0.12, 35.04233819928953)(0.125, 35.28459751937852)(0.13, 35.54051858700078)(0.135, 35.71160118222253)(0.14, 35.90299191316566)(0.145, 35.906383030560136)(0.15, 36.01964491090135)(0.155, 36.249355643497005)(0.16, 36.412319774410044)

@@

		\node [right] at (endofplotsquare) {$\scriptstyle n=300$};
(0.0, 9.572501789514533)(0.005, 30.95805680601551)(0.01, 31.852731472234083)(0.015, 31.651653530015025)(0.02, 31.83801995333023)(0.025, 31.805148564578964)(0.03, 32.04955343823956)(0.035, 31.874671808872318)(0.04, 31.962115616320467)(0.045, 32.18970870320976)(0.05, 32.29347571578702)(0.055, 32.32802283202089)(0.06, 32.32551565971646)(0.065, 32.51203709690735)(0.07, 32.671571263469616)(0.075, 33.00950294213178)(0.08, 32.921019505844626)(0.085, 33.01715330808184)(0.09, 33.11615572233624)(0.095, 33.39365131796149)(0.1, 33.19788472106813)(0.105, 33.45802024726345)(0.11, 33.5638596989855)(0.115, 33.685389159897156)(0.12, 33.74232351659747)(0.125, 33.86778330552731)(0.13, 34.01232127428546)(0.135, 34.31523066744031)(0.14, 34.360222768291344)(0.145, 34.357399370664666)(0.15, 34.42537992870109)(0.155, 34.521182964909315)(0.16, 34.6444682447327)(0.165, 34.79488974531291)(0.17, 34.972098710274665)(0.175, 35.175746041381494)(0.18, 35.29487711778767)
		\node [right] at (endofplotsquare) {$\scriptstyle n=500$};
(0.0, 5.787276464643081)(0.005, 30.032322717189135)(0.01, 31.072712082932913)(0.015, 30.438989170134064)(0.02, 31.078870323751065)(0.025, 31.034084842664363)(0.03, 30.826085689381884)(0.035, 31.04609765076408)(0.04, 31.154259509093443)(0.045, 31.016858116914054)(0.05, 31.183097869794107)(0.055, 31.225975525465568)(0.06, 31.23249090698877)(0.065, 31.428023434202135)(0.07, 31.489666903553392)(0.075, 31.561737353197035)(0.08, 31.761301359885042)(0.085, 31.729964289057)(0.09, 31.886510772066778)(0.095, 32.04347363722421)(0.1, 32.20435818840492)(0.105, 32.371965761927385)(0.11, 32.21538679904917)(0.115, 32.38001692151431)(0.12, 32.480852737576015)(0.125, 32.525780745561875)(0.13, 32.54658216492318)(0.135, 32.74841841730962)(0.14, 32.738242991760515)(0.145, 32.744293569773916)(0.15, 32.77968803547449)(0.155, 32.844022563820616)(0.16, 32.936888670494405)(0.165, 33.05787673349303)(0.17, 33.027986659386485)(0.175, 33.208654327237824)(0.18, 33.24666234435104)(0.185, 33.484850761982344)(0.19, 33.7582361354258)(0.195, 33.72513316286922)(0.2, 33.742552944335195)
		\node [below] at (endofplotsquare) {$\scriptstyle n=1000$};

@@

(0.0, 100.0)(0.005, 75.6291090455679)(0.01, 68.86366141298357)(0.015, 64.15161809404613)(0.02, 60.30668127053669)(0.025, 57.17914392613188)(0.03, 54.55578277664167)(0.035, 52.12060967528165)(0.04, 50.0814332247557)(0.045, 48.13910921293472)(0.05, 46.30180448145945)(0.055, 44.77126228174479)(0.06, 43.265700483091784)(0.065, 41.80088407592652)(0.07, 40.46538368433793)(0.075, 38.982235714929814)(0.08, 37.767521494770534)(0.085, 36.57442916986252)(0.09, 35.434337525592284)(0.095, 34.23204098688274)(0.1, 33.228055753852374)(0.105, 32.00063188430773)(0.11, 30.73345259391771)(0.115, 30.234530726493926)(0.12, 28.65745660644704)(0.125, 28.41693992883556)(0.13, 27.203065134099617)(0.135, 26.740179186767747)(0.14, 26.437563797209936)(0.145, 26.291079812206572)(0.15, 26.312314295146912)(0.155, 26.404676843130886)(0.16, 27.169094363521214)(0.165, 28.051787916152897)(0.17, 29.097992208570574)(0.175, 30.20954598370198)(0.18, 32.12290502793296)(0.185, 34.90216816499207)(0.19, 37.85536159600998)(0.195, 41.80895246885095)(0.2, 47.16356107660455)(0.205, 55.58231549974196)
			}node[pos=0.715](endofplotsquare){} ;
		\node [above] at (endofplotsquare) {$\scriptstyle n=50$};

@@

(0.0, 100.0)(0.005, 71.70551322277007)(0.01, 64.21561427636762)(0.015, 59.152215799614645)(0.02, 55.14354066985646)(0.025, 51.94629575968318)(0.03, 49.275021184445905)(0.035, 46.972740315638454)(0.04, 44.80417284949862)(0.045, 43.010835657359536)(0.05, 41.346756248784814)(0.055, 39.7071490094746)(0.06, 38.23283082077052)(0.065, 37.03703703703704)(0.07, 35.79600778967868)(0.075, 34.463684463684466)(0.08, 33.269969506158176)(0.085, 32.158590308370044)(0.09, 31.136680613668062)(0.095, 30.152342627191725)(0.1, 29.132513661202182)(0.105, 28.262910798122064)(0.11, 27.26222851395148)(0.115, 26.33194069582578)(0.12, 25.371764273912248)(0.125, 24.603463329452854)(0.13, 24.022145204122978)(0.135, 23.156745925250025)(0.14, 21.999107541276217)(0.145, 21.22984228247387)(0.15, 20.78947368421054)(0.155, 19.490781387181737)(0.16, 19.133486206656936)(0.165, 18.550474547023295)(0.17, 18.398637137989777)(0.175, 18.506084767100294)(0.18, 19.443307408923456)(0.185, 19.87127916331456)(0.19, 21.904024767801857)(0.195, 24.071322436849925)(0.2, 26.37949448202207)(0.205, 30.45212765957447)(0.21, 35.468130527599875)(0.215, 42.673452986873826)(0.22, 54.60844005878648)
			}node[pos=0.693](endofplotsquare){} ;
		\node [above] at (endofplotsquare) {$\scriptstyle n=75$};

@@

(0.0, 100.0)(0.005, 68.65666138131937)(0.01, 60.63128685397155)(0.015, 55.31576856878062)(0.02, 51.33935647487716)(0.025, 48.17702361843614)(0.03, 45.47825056299633)(0.035, 43.247126436781606)(0.04, 41.15998879237881)(0.045, 39.46929740660782)(0.05, 37.83422459893048)(0.055, 36.21545003543586)(0.06, 34.86767583153125)(0.065, 33.45501559053921)(0.07, 32.26047904191617)(0.075, 31.25)(0.08, 30.186491448449132)(0.085, 29.03995229576625)(0.09, 28.059248095512835)(0.095, 27.050610820244327)(0.1, 26.39724849527085)(0.105, 25.45442167608415)(0.11, 24.657534246575345)(0.115, 23.77777777777778)(0.12, 22.975352112676052)(0.125, 22.305764411027564)(0.13, 21.322987559061936)(0.135, 20.541178997100825)(0.14, 20.171546251671927)(0.145, 19.27825261158595)(0.15, 18.712795673051776)(0.155, 17.89802289281998)(0.16, 17.240096708201612)(0.165, 15.968992248062015)(0.17, 15.514592933947773)(0.175, 14.936914936914944)(0.18, 14.343434343434344)(0.185, 14.314214463840399)(0.19, 14.538310412573674)(0.195, 15.749162278602203)(0.2, 17.11627906976744)(0.205, 19.464285714285715)(0.21, 22.907861369399832)(0.215, 27.28706624605678)(0.22, 34.412385643912735)(0.225, 45.040840140023334)

@@

(0.0, 100.0)(0.005, 63.73968339872818)(0.01, 55.25949492940943)(0.015, 49.836271162823095)(0.02, 45.76241291119146)(0.025, 42.848738259828124)(0.03, 40.2020202020202)(0.035, 38.270402897591175)(0.04, 36.19752340682573)(0.045, 34.672815107597714)(0.05, 33.17294840951617)(0.055, 31.764378220303577)(0.06, 30.434782608695652)(0.065, 29.205903960462162)(0.07, 28.03868535365953)(0.075, 27.118862217645933)(0.08, 26.08420386198165)(0.085, 25.031172069825438)(0.09, 24.41860465116279)(0.095, 23.50749083447746)(0.1, 22.719556865898333)(0.105, 21.842863019333617)(0.11, 21.073630758070365)(0.115, 20.600858369098713)(0.12, 19.767935474741762)(0.125, 19.123511550785672)(0.13, 18.417662783772183)(0.135, 17.85180410603837)(0.14, 17.085768655702044)(0.145, 16.275049964889536)(0.15, 15.851899342843398)(0.155, 15.317031861966747)(0.16, 14.52991452991453)(0.165, 13.919031719532558)(0.17, 13.261072502852397)(0.175, 13.0033104934945)(0.18, 12.267278755419527)(0.185, 11.519029121283687)(0.19, 10.920446659516758)(0.195, 10.175879396984925)(0.2, 10.130515848353014)(0.205, 10.458715596330276)(0.21, 11.057692307692308)(0.215, 13.560300057703405)(0.22, 17.312943746586566)(0.225, 23.076923076923077)(0.23, 33.36203185535945)(0.235, 53.74149659863946)
		%\node [above] at (endofplotsquare) {$n=150$};
(0.0, 100.0)(0.005, 60.3675645342312)(0.01, 51.319740793425)(0.015, 46.22398877718026)(0.02, 42.248989357313754)(0.025, 39.48366318632798)(0.03, 36.95646756871247)(0.035, 34.86590038314176)(0.04, 33.287324591672416)(0.045, 31.549749463135292)(0.05, 30.303030303030305)(0.055, 28.925445534113674)(0.06, 27.7629141798724)(0.065, 26.898823151383702)(0.07, 25.83120204603581)(0.075, 24.751099791618426)(0.08, 23.846328711070697)(0.085, 22.90933467404057)(0.09, 22.152617503755)(0.095, 21.356421356421354)(0.1, 20.641965664778876)(0.105, 19.924470242674317)(0.11, 19.246298788694478)(0.115, 18.639682728804615)(0.12, 17.889352537353624)(0.125, 17.10362047440699)(0.13, 16.548704612042002)(0.135, 15.788444936719163)(0.14, 15.150341979610268)(0.145, 14.5667656734055)(0.15, 14.26135287058674)(0.155, 13.72303844951547)(0.16, 13.038076899186276)(0.165, 12.357716063644613)(0.17, 11.672407194795255)(0.175, 11.417322834645667)(0.18, 10.993035542747359)(0.185, 10.327952015756024)(0.19, 9.697508896797151)(0.195, 9.397944199706314)(0.2, 8.847889916297829)(0.205, 7.737226277372263)(0.21, 7.525325615050651)(0.215, 7.845934379457917)(0.22, 9.22970159611381)(0.225, 13.19763624425476)(0.23, 20.286396181384248)(0.235, 32.93591654247392)

@@

(0.0, 100.0)(0.005, 55.39254559873117)(0.01, 46.27647958069447)(0.015, 40.98883572567782)(0.02, 37.57387706855791)(0.025, 34.92709747016042)(0.03, 32.80632411067194)(0.035, 30.68683049779459)(0.04, 29.356357927786497)(0.045, 27.967337416156322)(0.05, 26.414400135850336)(0.055, 25.340360122968818)(0.06, 24.41984245262934)(0.065, 23.43230897009966)(0.07, 22.48062015503876)(0.075, 21.73374613003096)(0.08, 20.796890184645278)(0.085, 20.076344983895975)(0.09, 19.445222751470993)(0.095, 18.699186991869922)(0.1, 17.921584588251264)(0.105, 17.33511586452763)(0.11, 16.812609457092822)(0.115, 16.187842917008684)(0.12, 15.665729619217991)(0.125, 14.9634806036751)(0.13, 14.223850766155895)(0.135, 13.786008230452675)(0.14, 13.098339303158584)(0.145, 12.854905425484917)(0.15, 12.447885646217985)(0.155, 11.866540761724895)(0.16, 11.363060799096086)(0.165, 10.81081081081081)(0.17, 10.077459927908572)(0.175, 9.79381443298968)(0.18, 9.509058481179007)(0.185, 8.700522778192685)(0.19, 8.360485781990516)(0.195, 7.958553791887135)(0.2, 7.704070487147756)(0.205, 6.985161056822299)(0.21, 6.2404211968770875)(0.215, 6.123395977226902)(0.22, 5.431878895814782)(0.225, 6.036745406824147)(0.23, 7.731520815632965)(0.235, 15.277777777777779)(0.24, 32.60340632603406)
		%\node [above] at (endofplotsquare) {$n=300$};
(0.0, 100.00000000000001)(0.005, 48.82985928211302)(0.01, 40.20061728395061)(0.015, 35.8974358974359)(0.02, 32.10526315789474)(0.025, 29.89508775370134)(0.03, 27.69744160177975)(0.035, 26.26728110599078)(0.04, 24.878294443511834)(0.045, 23.238526179702653)(0.05, 22.453433091730965)(0.055, 21.28060263653484)(0.06, 20.47278564132497)(0.065, 19.744318181818187)(0.07, 18.640077551585644)(0.075, 17.62153366329921)(0.08, 17.41543340380549)(0.085, 16.612798965740136)(0.09, 16.096757852076994)(0.095, 15.320195510725066)(0.1, 15.115005476451262)(0.105, 14.304548450889916)(0.11, 13.963287073867834)(0.115, 13.283062645011602)(0.12, 12.95662100456622)(0.125, 12.517580872011251)(0.13, 12.032412032412036)(0.135, 11.314900744076228)(0.14, 10.927008880225257)(0.145, 10.857264866019005)(0.15, 10.408432147562582)(0.155, 10.170285892829245)(0.16, 9.619940261612939)(0.165, 9.276248725790005)(0.17, 8.879802110151953)(0.175, 8.181135851888914)(0.18, 7.840951319212183)(0.185, 7.44377884709809)(0.19, 7.141815353201405)(0.195, 6.774544137181501)(0.2, 6.297929447852767)(0.205, 5.965045592705168)(0.21, 5.580409700965386)(0.215, 5.32959326788219)(0.22, 4.6023546930988015)(0.225, 4.557714918044133)(0.23, 3.67816091954023)(0.235, 4.514672686230249)(0.24, 11.203319502074688)(0.245, 43.82314694408323)

@@

		\node [below left] at (endofplotsquare) {$\scriptstyle n=1000$};

@@

		\caption{The percent reduction in the 0.5 probability bound, that going from our EBB to Hoeffding's inequality (representing perfect knowledge of the variance, $\hat{\sigma}^2=\sigma^2$) achieves, for various $n=50,75,100,150,200,300,500,1000$.}
